### 2019-11-01 inst/README.rmd
adds make.R, renders and moves README.md

- [Rclean](https://github.com/ProvTools/Rclean) was created to help
  scientists more *easily* write "cleaner" code. 
- Written with research scientists that are results oriented in mind,
  the package's primary function provides a simple way to isolate the
  minimal code you need to produce a specific result, such as a
  statistical table or a figure.
- By focusing on specific results, large and/or complicated analytical
  scripts can be paired down to the essentials and easily re-factored
  to be more robust and easily shared.

>>>>

- [Rclean](https://github.com/ProvTools/Rclean) was created to help
  scientists more *easily* write "cleaner" code. 
- Written with research scientists that are results oriented in mind,
  the package's primary function provides a simple way to isolate the
  minimal code you need to produce a specific result, such as a
  statistical table or a figure.
- By focusing on specific results (aka. variables), large and/or
  complicated analytical scripts can be paired down to the essentials
  and easily re-factored to be more robust and easily shared.
